Irt plot extra

### 2022-09-19 manuscript_v2.Rmd
Intro comments

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (@bossini2006sensibilita) are a couple of self-report tools measuring visual light sensitivity. They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime. However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios. To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.

>>>>

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (@bossini2006sensibilita) are a couple of self-report tools measuring visual light sensitivity. They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime. However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations. To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.
